
\documentclass[10pt, conference, compsocconf,a4paper]{IEEEtran}

\RequirePackage{nybohansenPreamble}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}


\begin{document}
\title{Extending Mocapy++ with a mixed probability distribution\\Advanced Topics In Data Modeling}


\author{\IEEEauthorblockN{Kasper Nybo Hansen}
\IEEEauthorblockA{Dept. of Computer Science\\
University of Copenhagen\\
Copenhagen, Denmark\\
nybo@diku.dk}
}

% make the title area
\maketitle


add line to prog in cmakelist so it will be compiled

add your own folder describing node

open framework/dbn.h - add your new node



\begin{abstract}
The abstract goes here. DO NOT USE SPECIAL CHARACTERS, SYMBOLS, OR MATH IN YOUR TITLE OR ABSTRACT.

\end{abstract}

\begin{IEEEkeywords}
Mocapy++; DIKU; Dynamic Bayesian networks; Mixed probability distribution

\end{IEEEkeywords}


\section{Introduction}
Introduction

http://www.tutorvista.com/math/mixed-probability-distribution
http://www.freemathhelp.com/forum/viewtopic.php?f=12&t=34692

Good explanation
http://www.ds.unifi.it/VL/VL_EN/dist/dist3.html

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

\section{Type style and Fonts}
Wherever Times is specified, Times Roman or Times New Roman may be used. If neither is available on your system, please use the font closest in appearance to Times. Avoid using bit-mapped fonts if possible. True-Type 1 or Open Type fonts are preferred. Please embed symbol fonts, as well, for math, etc.

\section{Conclusion}
The conclusion goes here. this is more of the conclusion.


\section*{Acknowledgment}

The authors would like to thank...
more thanks here


\bibliographystyle{abbrv}
\bibliography{bibliography}


\end{document}


